Followers Are Not Enough: A Question-Oriented Approach to Community Detection

### 2014-07-31 paper-for_arxiv/paper.tex
fixing ordering and adding funding section

\section{Acknowledgments}

Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
Elisa Omodei is partially supported by a PhD grant from the Région Ile-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
We are grateful to DARPA for the support of David Darmon.

>>>>

\section{Funding}
Elisa Omodei is partially supported by a PhD grant from the Région Ile-de-France (DIM 2011) and by the French National Agency of Research (ANR) through the grant Algopol (ANR-12-CORD-0018).
We are grateful to DARPA for the support of David Darmon.
\section{Acknowledgments}

Thanks to Cesar Flores, Lu\'is Seoane, Kevin Stadler, Jody Wright, and Nix Barnett for their contributions to preliminary ideas related to this paper and to Michelle Girvan, William Rand, and Aaron Clauset for their valuable comments and suggestions.
